\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-10 paper.tex
Finish the theory of the attack current.

\notaL{Aquí voy. Checa la ecuación previa}

In our case of
interest we take $0\le z < z_0$ and thus write

  \begin{eqnarray}\label{Eq:EC11}
 \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} )
    +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg(
    e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0)
    \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}
At a height $ 0 <z <z_0 $ I simplify
   \begin{eqnarray}
 \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z
     +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x
     x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)
If the surface of the liquid is at a finite height c, then we can use images, like:
  \includegraphics[scale=.6]{Images/celd1}
  \caption{\emph{Diagram shows that there is a positive (real) plane $
      z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
      $) and its images are a positive plate at $ 2c-z_0 $ and a
      negative plate at $ 2c + z_0 $, the image is repeated vertically
      with the period $ L_z = 4c $}}
  \label{fig:Celda1}
In Fig. \ref{fig:Celda1} it is observed that there is a positive
(real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor
($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a
negative plate at $ 2c + z_0 $. Also, the image is repeated vertically
with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11}
would be rewritten, like this
 \begin{eqnarray}\label{Eq:EC1}
 \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n}
   -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg)
   +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg(
   \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}}
   +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}
   \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot
   \vec{r}}\\
The constant K is chosen thus $ \phi (z = 0) $, substituting in
Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are
explicitly left with the geometric sum over $n$
{\small
  \begin{eqnarray}
    \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  +
    \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0}
    \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz)
    \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} -
    e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
    y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\
}
Evaluating for $ z = 0 $
 \begin{eqnarray}\label{Eq:EC2}
\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  +
   \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc}
   \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
   y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber =
   K+\dfrac{16\pi q}{A} \\
Independent of $ x $ and $ y $ to configure
 \begin{eqnarray}
 K=\dfrac{16\pi q}{A}
I can further simplify Eq. (\ref {Eq:EC2}) to get,
 \begin{eqnarray}
\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  +
   \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0}
   -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg)
   \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
I am sure it is correct. Then it goes to zero at $ z = 0 $. The term
with c disappears if $ c \longrightarrow \infty $. The sum converges
when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z
\longrightarrow z_0 $. So it seems ready for calculation.
The normal component of the field is
\begin{eqnarray}
\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  +
  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0}
  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
And the current density is for any $ z $, for our calculation we
choose that $ z = 0 $
\begin{eqnarray}\label{Eq:J}
\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  +
  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0}
  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\
Integrating on the surface of the sample is obtained $I_{nm}
=\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$
\begin{eqnarray}
\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\
  I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)
Using the factor of the reciprocal vector in this way $ \vec {G} =
\bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in
\ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n
and m, only the constant term taxpayer to the integrated current
\begin{eqnarray}
\nonumber I^{nm} =\int \vec{J} dx  dy =-\int \vec{J}_\perp dx  dy=\dfrac{I}{ab}\int dx \int dy=I
\subsection{Transfer Matrix Method (TMM)}
One of the methods used for the analysis of photonic crystal
structures is the transfer matrix method. We use it to investigate the
reflectance of light in a one-dimensional photonic crystal. The
electric and magnetic fields within the layers are shown as $E_m$ and
$H_m$. Then we can specify the electric and magnetic fields in the
air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
\left[
\begin{matrix}
E_{_{0}}\\
H_{_{0}}
\end{matrix}
\right]= \textbf{M}_{_{1}}, \textbf{M}_{_{2}},...,\textbf{M}_{_{N}} \left[
\begin{matrix}
E_{_{m}}\\
H_{_{m}}
\end{matrix}
\right]
Where N is the total number of layers including the cavity layer and $
M_j $ is the matrix characteristic of the layer $ j $ specified by:
\textbf{M}_j = \left[
\begin{matrix}
\cos \delta_j & -\frac{i}{\eta_j} \sin \delta_j \\
-i\eta_j \sin\delta_j & \cos\delta_j
\end{matrix}
\right]
\delta_j= \frac{2\pi}{\lambda} \tilde{n}_j d_j \cos \theta_j
where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
is the thickness of the layer, and $ \theta_j $ is the angle of
refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
for layer j is defined as:
\begin{equation}\label{Eq:Mt1}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}}\tilde{n}_j cos\theta_j \hspace{1cm} (TE \ \ mode)
y
\begin{equation}\label{Eq:Mt2}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}} \frac{\tilde{n}_j}{cos\theta_j} \hspace{1cm} (TM \ \ mode)
where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
permeability, respectively. The transfer matrix of all the photonic
crystal is given by:
\textbf{M}=\textbf{M}_1,\textbf{M}_2,...,\textbf{M}_N= \left[
\begin{matrix}
m_{11} & m_{12} \\
m_{21} & m_{22}
\end{matrix}
\right]
We can write the reflection and transmission coefficients in a
one-dimensional photonic crystal nanocavity as:
r=\frac{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}
end
t=\frac{2\eta_0}{\eta_0(m_{11}m_{12}\eta_m)+(m_{21}m_{22}\eta_m)}
where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
layers, respectively (as defined in equations \ref{Eq:Mt1} or
\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
the entire photonic crystal nanocavity is given by:
R=|r|^{2}
y
T=\frac{\eta_m}{\eta_0}|t|^{2}
\section{Experimental Details}
  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for
      fabrication of porous silicon with GRIN. (a) Represents an
      outline of the surface section, divided by three regions
      A, B and C, corresponding to High, Medium and Low Porosity
      respectively. (b) It is the diagram of the electrochemical
      cell with its parts: silicon wafer, Teflon cell, platinum
      point electrode, Electrochemical Aqueous solution and the
      connection of the circuit with the cathode and anode. (c)
      It is a schematic drawing of the Cross section of the
      electrochemically attacked porous silicon seen in three
      different regions as mentioned above. }}
    \label{fig:DE1}

>>>>

Notice that the terms of the sum above converge exponentially to zero
as $G$ increases for any $z$ such that $0\le z <z_0 \le c$, and thus
the sum is convergent. The divergence in the limit $ z
\longrightarrow z_0 $ is not worrisome, as we are interested in the
field close to bottom $z=0$ of the cell.

The current density normal to the surface may now be obtained as
$j_\perp=-\sigma\partial\phi/\partial z$,
\begin{equation}
  \label{Eq:J}
  \begin{split}
    j_\perp(\bm r) =& -\frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
      Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
    &\times \cosh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
  \end{split}
\end{equation}
Eq. \eqref{Eq:J} is a very rapidly convergent expression that allows,
in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
the substrate to produce the PS sample.
Integrating over the surface of the sample we verify
\begin{equation}
  \label{eq:intj}
  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=-I,
\end{equation}
as the contributions of opposite non-null reciprocal vectors cancel
out. As expected, all of the current that leaves the electrode find
its way to the substrate.

\subsection{Transfer Matrix Method (TMM)}
One of the methods used for the analysis of photonic crystal
structures is the transfer matrix method. We use it to investigate the
reflectance of light in a one-dimensional photonic crystal. The
electric and magnetic fields within the layers are shown as $E_m$ and
$H_m$. Then we can specify the electric and magnetic fields in the
air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:
\begin{equation}
\left[
\begin{matrix}
E_{_{0}}\\
H_{_{0}}
\end{matrix}
\right]= \textbf{M}_{_{1}}, \textbf{M}_{_{2}},...,\textbf{M}_{_{N}} \left[
\begin{matrix}
E_{_{m}}\\
H_{_{m}}
\end{matrix}
\right]
\end{equation}
Where N is the total number of layers including the cavity layer and $
M_j $ is the matrix characteristic of the layer $ j $ specified by:
\begin{equation}
\textbf{M}_j = \left[
\begin{matrix}
\cos \delta_j & -\frac{i}{\eta_j} \sin \delta_j \\
-i\eta_j \sin\delta_j & \cos\delta_j
\end{matrix}
\right]
\end{equation}
and
\begin{equation}
\delta_j= \frac{2\pi}{\lambda} \tilde{n}_j d_j \cos \theta_j
\end{equation}
where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
is the thickness of the layer, and $ \theta_j $ is the angle of
refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
for layer j is defined as:
\begin{equation}\label{Eq:Mt1}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}}\tilde{n}_j cos\theta_j \hspace{1cm} (TE \ \ mode)
\end{equation}
y
\begin{equation}\label{Eq:Mt2}
\eta_j=\sqrt{\frac{\epsilon_0}{\mu_0}} \frac{\tilde{n}_j}{cos\theta_j} \hspace{1cm} (TM \ \ mode)
\end{equation}
where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
permeability, respectively. The transfer matrix of all the photonic
crystal is given by:
\begin{equation}
\textbf{M}=\textbf{M}_1,\textbf{M}_2,...,\textbf{M}_N= \left[
\begin{matrix}
m_{11} & m_{12} \\
m_{21} & m_{22}
\end{matrix}
\right]
\end{equation}
We can write the reflection and transmission coefficients in a
one-dimensional photonic crystal nanocavity as:
\begin{equation}
r=\frac{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}
\end{equation}
end
\begin{equation}
t=\frac{2\eta_0}{\eta_0(m_{11}m_{12}\eta_m)+(m_{21}m_{22}\eta_m)}
\end{equation}
where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
layers, respectively (as defined in equations \ref{Eq:Mt1} or
\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
the entire photonic crystal nanocavity is given by:
\begin{equation}
R=|r|^{2}
\end{equation}
y
\begin{equation}
T=\frac{\eta_m}{\eta_0}|t|^{2}
\end{equation}
\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for
      fabrication of porous silicon with GRIN. (a) Represents an
      outline of the surface section, divided by three regions
      A, B and C, corresponding to High, Medium and Low Porosity
      respectively. (b) It is the diagram of the electrochemical
      cell with its parts: silicon wafer, Teflon cell, platinum
      point electrode, Electrochemical Aqueous solution and the
      connection of the circuit with the cathode and anode. (c)
      It is a schematic drawing of the Cross section of the
      electrochemically attacked porous silicon seen in three
      different regions as mentioned above. }}
    \label{fig:DE1}
  \end{figure}
